Untitled

### 2020-05-11 results/README.Rmd

# function that reads results for a model M 
read_results <- function(m){
   files = list.files(paste0("/Volumes/Gerbrich/asreview/results/one_seed/statistics/", m), recursive = TRUE)
  # names of the files are the data
  names(files) <- str_split(files, "/", simplify = TRUE)[,1]
  # read data
  dat <- lapply(files, function(x) fromJSON(file = paste0("/Volumes/Gerbrich/asreview/results/one_seed/statistics/", m, "/", x)))

@@

  return(dat)
}
```

@@

# convert loss (ttd) to percentage 
results$loss <- results$loss*100
# save results file 
saveRDS(results, "output/results.RDS")

@@

tab <- 
  test %>%
  tab_rows(model) %>%
  tab_cells(value) %>%
  tab_cols(dataset %nest% stats) %>%
  tab_stat_mean() %>%
  tab_pivot()

@@

```{r}
stabres <- 
tabres %>%
  select(model,
         starts_with("wss.95"),
         starts_with("rrf.10"), 
         starts_with("loss")) %>%
  select(model,
         ends_with("ace"),
         ends_with("nudging"),
         ends_with("ptsd"),
         ends_with("software"),
         ends_with("virus"),
         ends_with("wilson")
         )

@@

metricsat <- c("WSS@95", "RRF@10", "TTD")
metrics <- c("WSS", "RRF", "TTD")
at <- c("@95", "@10", "")

@@

test
test <- merge_h(test, part = "header")
test
#border_v = fp_border(color="purple")
#test <- border_inner_v(test, part="all", border = border_v )
test <- merge_v(test, part = "header")

test

test <- theme_booktabs(test)
test <- autofit(test, add_w = 0.2)
test <- fix_border_issues(test)

test
test <- align(test, align = "left", part = "all" )
test
```

>>>>

# function that reads results for a model M 
read_results <- function(m){
   files = list.files(paste0("/Volumes/Gerbrich/asreview/results/one_seed/statistics/", m), pattern = "all.json", recursive = TRUE)
  # names of the files are the data
  names(files) <- str_split(files, "/", simplify = TRUE)[,1]
  # read data
  dat <- lapply(files, function(x) fromJSON(file = paste0("/Volumes/Gerbrich/asreview/results/one_seed/statistics/", m, "/", x)))

@@

  return(dat)
}

read_trials <- function(m){
   files <- list.files(paste0("/Volumes/Gerbrich/asreview/results/one_seed/statistics/", m), pattern = "results_", recursive = TRUE, full.names=TRUE)
  # names of the files are the data
  names(files) <- str_split(files, "/", simplify = TRUE)[,9]
  # read data

  dat <- lapply(files, function(x) fromJSON(file = x))
  # dat <- lapply(models, list)
  # dat <- lapply(files, function(x) fromJSON(file = paste0("/Volumes/Gerbrich/asreview/results/one_seed/statistics/", m, "/", x)))

  return(dat)
}

datastats <- readRDS("datastats.RDS") %>%
  select(Dataset, candidates_test, incl_test) %>%
  mutate(n_1 = incl_test, n_excl = candidates_test-n_1, n_1_noprior = incl_test-1, candidates_noprior = candidates_test -1) %>%
  mutate(ratio = (n_1_noprior/n_1)/(candidates_noprior/candidates_test))
# account for 1 prior exclusion

datastats$dataset <- c("ace", "nudging", "ptsd", "software", "virus", "wilson")
atdratio <- datastats %>%
  select(dataset, ratio)

```{r}
runs <- lapply(models, FUN = read_trials)

# all in one dataframe
runs <- do.call("rbind", runs)

# convert loss (ttd) to percentage 
runs$loss <- runs$loss*100
# adjust loss to N_1 : N_1-1
runs <- left_join(runs, atdratio, by = "dataset")

runs <- runs %>%
  mutate(loss = loss/ratio) %>%
  select(-ratio)

# save results file 
saveRDS(runs, "output/runs.RDS")
```

```{r}
# compute standard devaition (bootstrapped)
test <- 
  runs %>%
  select(dataset, model, wss.95, rrf.10, loss)

# compute bootstrap statistics 
library(boot)

bootmeans <- function(d,i){
  d2 <- d[i,]

  # result <- d2 %>%
  #   group_by(model, dataset) %>%
  #   summarise(meanwss = mean(wss.95),
  #             meanrrf = mean(rrf.10), 
  #             meanloss = mean(loss))
  wss <- mean(d2[, "wss.95"])
  rrf <- mean(d2[, "rrf.10"])
  loss <- mean(d2[, "loss"])

  return(c(wss,rrf,loss))
}
res <- boot(test, bootmeans, 1000)

test <- 
  runs %>%
  select(dataset, model, wss.95, rrf.10, loss) %>% 
  group_by(model, dataset) %>%
  summarise(sdwss.95 = sd(wss.95),
            sdrrf.10 = sd(rrf.10),
            sdloss = sd(loss))

saveRDS(test, "output/sdruns.RDS")
```

```{r}
# sumruns <- runs %>%
#   group_by(dataset, model) %>%
#   summarise(mean_wss95 = mean(wss.95),
#             sd_wss95 = sd(wss.95), 
#             mean_wss99 = mean(wss.99),
#             sd_wss99= sd(wss.99),
#             mean_wss100 = mean(wss.100),
#             sd_wss100 = sd(wss.100), 
#             mean_rrf5 = mean(rrf.5),
#             sd_rrf5 = sd(rrf.5),
#             mean_rrf10 = mean(rrf.10),
#             sd_rrf10 = sd(rrf.10), 
#             mean_rrf20 = mean(rrf.20),
#             sd_rrf20 = sd(rrf.20),
#             mean_loss = mean(loss),
#             sd_loss = sd(loss)) %>%
#   arrange(mean_loss)

# saveRDS(sumruns, "output/sumruns.RDS")
```

@@

# convert loss (ttd) to percentage 
results$loss <- results$loss*100
# adjust loss to N_1 : N_1-1
results <- left_join(results, atdratio, by = "dataset")

results <- results %>%
  mutate(loss = loss/ratio) %>%
  select(-ratio)

# save results file 
saveRDS(results, "output/results.RDS")

@@

library(expss)
tab <- 
  test %>%
  tab_rows(model) %>%
  tab_cells(value) %>%
  tab_cols(dataset %nest% stats) %>%
  tab_stat_mean() %>%
  tab_pivot()

@@

```{r}
stabres <- 
tabres %>%
  select(model,
         starts_with("wss.95"),
         starts_with("rrf.10"), 
         starts_with("loss")) %>%
  select(model,
         ends_with("nudging"),
         ends_with("ptsd"),
         ends_with("software"),
         ends_with("ace"),
         ends_with("virus"),
         ends_with("wilson")
         )

@@

```{r}
metricsat <- c("WSS@95", "RRF@10", "TTD")
metrics <- c("WSS", "RRF", "TTD")
at <- c("@95", "@10", "")

@@

test <- merge_h(test, part = "header")

#border_v = fp_border(color="purple")
#test <- border_inner_v(test, part="all", border = border_v )
test <- merge_v(test, part = "header")
test <- theme_booktabs(test)
test <- autofit(test, add_w = 0.2)
test <- fix_border_issues(test)

test <- align(test, align = "left", part = "all" )
